\documentclass[a5paper]{memoir}
\usepackage[autocompile]{gregoriotex}
\usepackage{libertine}
\usepackage{paracol}
\settypeblocksize{170mm}{108mm}{*} % Was 101mm in a5
\setulmargins{*}{*}{1.4}
\setlrmargins{*}{*}{1.2}
\setheadfoot{\onelineskip}{2\onelineskip}
\setheaderspaces{*}{.8\onelineskip}{*}
\checkandfixthelayout

\tolerance=5000
\pretolerance=3000

\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\parindent}{0pt}
\setlength{\stanzaskip}{6pt plus 2pt minus 1pt}



\begin{document}

\pagestyle{empty}

\begin{center}
	\textsc{\LARGE Prayer Before Choir Practice}

\smallskip 

	\textit{Oratio Ante Scholam Musicae}
\end{center}

{
	\fontsize{12}{14}\selectfont

\gregorioscore{va--repleatur}

}

\bigskip

[Let my mouth be filled with Thy praise, in order that I be able to sing; my lips will rejoice for as long as I sing unto Thee.]

\bigskip

\begin{paracol}{2}

\Vbar.	Laudábo Dóminum in vita mea.

	\switchcolumn

	I will give praise unto the Lord in my life.

	\switchcolumn*


\Rbar. Psallam Deo meo quámdiu ero.

	\switchcolumn

	I will sing psalms unto my God as long as I live.

	\switchcolumn*



Orémus.

	\switchcolumn

	Let us pray.

	\switchcolumn*



Súscipe, quaésumus, Dómine, sacrifícium labiórum nostrórum: \GreDagger\ 
et intercedéntibus sanctis tuis Gregório atque Caecília, 
	tua nobis pietáte concéde; 
	ut quam offérimus laudem perigrinántes in terris, \GreStar\ 
	hanc tibi perpétuo concinére mereámur in caelis. 
Per Christum Dóminum nostrum.
Amen.

	\switchcolumn

	Accept, we beseech Thee, O Lord, the sacrifice (homage) of our lips, \GreDagger\
	and through the intercession of thy saints, Gregory and Cecilia, 
	grant unto us Thy mercy; 
	that through these offerings of praise during our earthly pilgrimage, \GreStar\ 
	we may be found worthy to sing Thy praises eternally in heaven. 
	Through Christ our Lord. Amen.

\end{paracol}

\end{document}
